---
title: "FinalProjectRHere"
author: "Julia Baumohl"
format: html
execute: 
  echo: false
---


```{r}
#| output: false
library(tidyverse)
library(gtsummary)
install.packages("here")
library(here)

setwd("/Users/juliabaumohl/Library/CloudStorage/OneDrive-Emory/EPI 590 R Bootcamp/EPI590R Final Project")

load(here("covid_testing.rda"))
					
covid_testing$gender_num <- ifelse(covid_testing$gender == "female",1,0)
covid_testing$result_num <- ifelse(covid_testing$result == "negative",0,
																	 ifelse(covid_testing$result == "positive", 1, NA))

```

# Data Background:			

This data set is from Amrom E. Obstfeld, who de-identified data on COVID-19 testing during 2020 at CHOP (Children’s Hospital of Pennsylvania). This data set contains data concerning testing for SARS-CoV2 via PCR as well as associated metadata including names, ages, genders, day of pandemic testing took place, clinic names, etc. The data has been anonymized, time-shifted, and permuted. There were `r nrow(covid_testing)` participants.

# Table 1

```{r}
#| label: table-one
#| tbl-cap: "This table 1 is not inclusive of all variables in the data set, only of variables included in the regression."
table1 <- tbl_summary(
	covid_testing,
	by = result,
	include = c(gender,age,pan_day),
label = list(
	gender ~ "Gender",
	age ~ "Age (Years)",
	pan_day ~ "Day after start of pandemic in which specimen was collected"
))
table1
```

The IQR for age of invalid tests is `r inline_text(table1, variable = "age", column = "stat_1")`.

# Regression

```{r}
#|label: uvregression
#|tbl-cap: This regression analysis is not to be interpreted scientifically, and only conducted for coding practice purposes.

regression <- tbl_uvregression(
	covid_testing,
	y = result_num,
	include = c(gender_num, age, pan_day),
	method = glm,
	method.args = list(family = binomial()),
	exponentiate = TRUE)
regression

```

The @uvregression only had one statistically significant characteristic, which was age.

# Histogram of Day in Pandemic Testing Occured

```{r}
#| label: histpanday
#| fig-cap: "This table examines the number of COVID-19 tests daily in the data set after the pandemic began."
hist(covid_testing$pan_day)

```

The @histpanday varied throughout the pandemic. 

```{r}
#| output: false

max_minus_min <- function(x){
	maxminfunct <- max(x, na.rm = FALSE) - min(x, na.rm = FALSE)
	return(maxminfunct)
}
max_minus_min(x = covid_testing$pan_day)

```
